Spatial variation of coronal Fourier power spectra

### 2016-07-29 tex/paper2/paper2.tex
more edits to the paper, and adding in some code

The data was prepared for analysis using the SolarSoft / IDL routines
READ\_SDO and AIA\_PREP.  These procedures convert the downloaded
level 1.0 FITS cutout files to level 1.5 FITS files.  This involves
translating, scaling and rotating the images so they have the same
sun-center, image scale with solar north in the same direction.  All
further processing from this point was performed in the SunPy 0.7.???
(http://www.sunpy.org) data analysis environment.  Images were
de-rotated to compensate for solar rotation, based on the center of
the field of view of each image.  After de-rotation, each image layer
was coaligned with a reference layer, defined to be half way through
the dataset, in this case at approximately 03:00 UT.  This process is
required since the solar de-rotation function used does not fully
compensate for all the solar rotation. Image coalignment was
implemented using a template matching technique \citep{lewis1995fast}
implemented by the {\it scikit-image} \citep{Vanderwalt2014} routine
{\it match\_template}.  A rectangular template sub-image with sides
one half the size (in pixels) of the reference layer is defined.  The
coalignment algorithm finds the location of the best match of this
template with each layer.  The image layer is then shifted (using
sub-pixel shifts) according to the location of the best match of the
template with the image.  This process removes residual bulk motions
of the images.

@@

\subsection{Fitting the data}\label{sec:app:fit}
Section \ref{???} describes two models of the Fourier power spectrum.
These models are fit to the observed Fourier power spectrum as
described in Section \ref{}.  \Fpa\ models are fit by first generating
an estimate of the model parameters.  This estimate is used as an
initial guess to a fitting routine.

@@

Model fitting was initialized using the initial estimates described
above.  Models were fit by varying the value of model parameters in
order to find the maximum of the log of likelihood of the data given
the model.  If the time-series data are subject to a Gaussian noise,
then the Fourier power components are exponentially distributed.  Let
us assume that $I_{j}$ is the observed Fourier power at the frequency
indexed by $j$, and $S_{j}$ is the model Fourier power at that same
frequency.  The probability of an observed power $I_{j}$ given a model
power $S_{j}$ is given by
\begin{equation}
p_{j}\left(I_{j}|S_{j}\right) =
\frac{1}{S_{j}}\exp\left[-\frac{I_{j}}{S_{j}}\right]
\label{eqn:freqprob}
\end{equation}
If there are $N$ non-zero Fourier frequencies then the likelihood over
all frequencies is
\begin{equation}
L=\prod_{j=1}^{N}p\left(I_{j}|S_{j}\right)
\label{eqn:freqprob:all}
\end{equation}
The Nelder-Mead method was used to vary model parameters in search of
the maximum of the log likelihood.  The full code used (and the
history of its development) is availble as a git repository at
https://github.com/wafels/rednoise/tree/perpixel.

@@

\subsection{Calculating the 95\% confidence level using the $\chi^{2}$
analog}\label{sec:app:chi}

\subsection{Acceptable parameter limits}\label{sec:app:limit}

>>>>

The data was prepared for analysis using the SolarSoft / IDL routines
READ\_SDO and AIA\_PREP.  These procedures convert the downloaded
level 1.0 FITS cutout files to level 1.5 FITS files.  This involves
translating, scaling and rotating the images so they have the same
sun-center, image scale with solar north in the same direction.  All
further processing from this point was performed using SunPy 0.7
(http://www.sunpy.org) running under Python 3.5.

Images were
de-rotated to compensate for solar rotation, based on the center of
the field of view of each image.  After de-rotation, each image layer
was coaligned with a reference layer, defined to be half way through
the dataset, in this case at approximately 03:00 UT.  This process is
required since the solar de-rotation function used does not fully
compensate for all the solar rotation. Image coalignment was
implemented using a template matching technique \citep{lewis1995fast}
implemented by the {\it scikit-image} \citep{Vanderwalt2014} routine
{\it match\_template}.  A rectangular template sub-image with sides
one half the size (in pixels) of the reference layer is defined.  The
coalignment algorithm finds the location of the best match of this
template with each layer.  The image layer is then shifted (using
sub-pixel shifts) according to the location of the best match of the
template with the image.  This process removes residual bulk motions
of the images.

@@

\subsection{Fitting the data}\label{sec:app:fit}
Section \ref{sec:anal} describes two models of the Fourier power
spectrum that are fit to the observed Fourier power spectrum
\Fpa\ models are fit by first generating an estimate of the model
parameters.  This estimate is used as an initial guess to a fitting
routine.

@@

Model fitting was initialized using the initial estimates described
above.  Models were fit by varying the value of model parameters in
order to find the maximum of the log of likelihood of the data given
the model.  If the time-series data are subject to a Gaussian noise,
then the Fourier power components are exponentially distributed.  Let
us assume that $I_{j}$ is the observed Fourier power at the frequency
indexed by $j$, and $S_{j}$ is the model Fourier power at that same
frequency.  The probability of an observed power $I_{j}$ given a model
power $S_{j}$ is given by
\begin{equation}
p_{j}\left(I_{j}|S_{j}\right) =
\frac{1}{S_{j}}\exp\left[-\frac{I_{j}}{S_{j}}\right]
\label{eqn:freqprob}
\end{equation}
If there are $N$ non-zero Fourier frequencies then the likelihood over
all frequencies is
\begin{equation}
L=\prod_{j=1}^{N}p\left(I_{j}|S_{j}\right)
\label{eqn:freqprob:all}
\end{equation}
The Nelder-Mead method was used to vary model parameters in search of
the maximum of the log likelihood.  The full code used (and the
history of its development) to generate the results in this paper is
available as a git repository at
https://github.com/wafels/rednoise/tree/perpixel.

@@

\subsection{Calculating the 95\% confidence interval using the $\chi^{2}$
analog}\label{sec:app:chi} The fitting process finds model parameter
values that approximate the shape of the \Fps.  Noise in \Fps\ is
exponentially distributed, and so the reduced-$\chi^{2}$ measure
cannot be used to assess how well the model fits the
data. \citet{2014ApJ...789..152N} derive an analogous
reduced-$\chi^{2}$ for exponentially distributed data such as \Fpa.
Expected values of the reduced-$\chi^{2}$ analogue are calculated by
inverting Equation 18 of \citet{2014ApJ...789..152N} to make the
reduced-$\chi^{2}$ analogue the subject of the equation.  The 95\%
confidence interval is found by calculating the values of the
reduced-$\chi^{2}$ analogue that exclude the top and bottom 2.5\% of
the probability density function (Equation 18,
\citet{2014ApJ...789..152N}).

\subsection{Acceptable parameter limits}\label{sec:app:limit}
Even after the filtering process described in Section \ref{sec:anal},
the fitting algorithm still finds values which are probably outliers.
In order to present the vast majority of the results, limits are set
to the model parameters.  If any of the model parameters violate these
limits, the model fit to the data is classed as a bad fit and is not
considered further.  The table below lists the range of parameter
values, and gives the percentage of the model fits which violate these
limits as a function of AIA channel.  The fraction is calculated as
the number of model fits that violate these limits divided by the
total number of model fits.

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize} \tablecolumns{5} \tablewidth{0pt}
\tablecaption{Acceptable parameter ranges and the fraction of model
  fits that exceed the parameter ranges.  Section \ref{sec:anal} describe the meaning of each parameter value\label{tab:acceptable}}
\tablehead{
  \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range} & \multicolumn{6}{c}{AIA channel}\\
  \colhead{ } & \colhead{ } & \colhead{94\AA} & \colhead{131\AA} & \colhead{171\AA} & \colhead{193\AA}  & \colhead{211\AA} & \colhead{335\AA} \\ }
\startdata 
$A$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$n$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$C$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$\alpha$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$\log_{10}(\beta)$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$\log_{10}(\delta)$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.

\end{deluxetable}
